### 2020-08-15 README.Rmd
update README
add RepeatedSptCVCstf

<!-- badges: start -->
[![tic](https://github.com/mlr-org/mlr3spatiotempcv/workflows/tic/badge.svg?branch=master)](https://github.com/mlr-org/mlr3spatiotempcv/actions)
[![CRAN Status Badge](https://www.r-pkg.org/badges/version-ago/mlr3spatiotempcv)](https://cran.r-project.org/package=mlr3spatiotempcv)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotempcv/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotempcv?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

@@

⚠️⚠️⚠️  
The package is in very early stages and breaking changes withour further notice are expected.
If you want to use if for your research, you might need to refactor your analysis along the way.  
⚠️⚠️⚠️

@@

| Literature                  | Package    | Reference     | mlr3 Sugar                     |
| --------------------------- | ---------- | ------------- | ------------------------------ |
| Spatial Buffering           | blockCV    | Valavi 2019   | `rsmp("spcv-buffer")`          |
| Spatial Blocking            | blockCV    | Valavi 2019   | `rsmp("spcv-block")`           |
| Spatial CV                  | sperrorest | Brenning 2012 | `rsmp("spcv-coords")`          |
| Environmental Blocking      | blockCV    | Valavi 2019   | `rsmp("spcv-env")`             |
| -                           | -          | -             | `rsmp("sptcv-cluto")`          |
| Leave-Location-and-Time-Out | CAST       | Meyer 2018    | `rsmp("sptcv-cstf")`           |
| ---                         | ---        | ---           | ---                            |
| Repeated Spatial Blocking   | blockCV    | Valavi 2019   | `rsmp("repeated-spcv-block")`  |
| Repeated Spatial CV         | sperrorest | Brenning 2012 | `rsmp("repeated-spcv-coords")` |
| Repeated Env Blocking       | blockCV    | Valavi 2019   | `rsmp("repeated-spcv-env")`    |
| -                           | -          | -             | `rsmp("repeated-sptcv-cluto")` |

@@

| Name     | Code              | Type    |
| ---      | ---               | ---     |
| ecuador  | `tsk("ecuador")`  | Classif |
| diplodia | `tsk("diplodia")` | Classif |

@@

| Name     | Code              | Type    |
| ---      | ---               | ---     |
| cookfarm | `tsk("cookfarm")` | Regr    |

@@

Generic S3 function `autoplot()` for all implemented spatial resampling methods.

>>>>

<!-- badges: start -->

[![tic](https://github.com/mlr-org/mlr3spatiotempcv/workflows/tic/badge.svg?branch=master)](https://github.com/mlr-org/mlr3spatiotempcv/actions) [![CRAN Status Badge](https://www.r-pkg.org/badges/version-ago/mlr3spatiotempcv)](https://cran.r-project.org/package=mlr3spatiotempcv) [![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotempcv/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotempcv?branch=master) [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) <!-- badges: end -->

@@

⚠️⚠️⚠️\
The package is in very early stages and breaking changes withour further notice are expected. If you want to use if for your research, you might need to refactor your analysis along the way.\
⚠️⚠️⚠️

@@

| Literature                           | Package    | Reference     | mlr3 Sugar                     |
|--------------------------------------|------------|---------------|--------------------------------|
| Spatial Buffering                    | blockCV    | Valavi 2019   | `rsmp("spcv-buffer")`          |
| Spatial Blocking                     | blockCV    | Valavi 2019   | `rsmp("spcv-block")`           |
| Spatial CV                           | sperrorest | Brenning 2012 | `rsmp("spcv-coords")`          |
| Environmental Blocking               | blockCV    | Valavi 2019   | `rsmp("spcv-env")`             |
| \-                                   | \-         | \-            | `rsmp("sptcv-cluto")`          |
| Leave-Location-and-Time-Out          | CAST       | Meyer 2018    | `rsmp("sptcv-cstf")`           |
| ---                                  | ---        | ---           | ---                            |
| Repeated Spatial Blocking            | blockCV    | Valavi 2019   | `rsmp("repeated-spcv-block")`  |
| Repeated Spatial CV                  | sperrorest | Brenning 2012 | `rsmp("repeated-spcv-coords")` |
| Repeated Env Blocking                | blockCV    | Valavi 2019   | `rsmp("repeated-spcv-env")`    |
| \-                                   | \-         | \-            | `rsmp("repeated-sptcv-cluto")` |
| Repeated Leave-Location-and-Time-Out | CAST       | Meyer 2018    | `rsmp("repeated-sptcv-cstf")`  |

@@

| Name     | Code              | Type    |
|----------|-------------------|---------|
| ecuador  | `tsk("ecuador")`  | Classif |
| diplodia | `tsk("diplodia")` | Classif |

@@

| Name     | Code              | Type |
|----------|-------------------|------|
| cookfarm | `tsk("cookfarm")` | Regr |

@@

S3 `autoplot()` for all implemented spatial resampling methods.
